Realistically Interesting Domains for Probabilistic Planners

### 2014-04-08 FinalPaper/paper.tex

In sections above we have described the GOURMAND planner and FF-Replan as two
probabilistic planners of the IPPC competition.
RFF~\cite{teichteil2010incremental} is an offline planner that generates a
policy: for each reachable state it determines a plan to the goal. Like
FF-Replan it uses determinization and FF\. FF returns an initial plan from the
initial state to a goal state. For each state in the plan the successor states
are added to the structure, after which Monte-Carlo sampling is used. States
where the probability that they're reached is too low (below a threshold) are
removed. The successor states are used as initial states in the next step. If
FF fails to find a plan to the goal from this new state, the state is removed
from the structure too. Results showed that RFF outperformed other competitors.
A higher threshold means that RFF will generate more policies that are prone to
replanning.

>>>>

\subsubsection{RFF}. Also uses an incremental plan aggregation, but offline similar to \textsc{Glutton}.
